\begin{thebibliography}{99}
\raggedright
% reference in chapter 2
\bibitem{automatedmedical}
K. Rarhi \textit{et al.}, (2017, Jan). \enquote{Automated Medical Chatbot}.
\textit{SSRN Electronic Journal}. [Online].
Available: \url{https://ssrn.com/abstract=3090881}

\bibitem{superagent}
L. Cui \textit{et al.},
\enquote{SuperAgent: A Customer Service Chatbot for E-commerce Websites},
in \textit{ACL 2017, System Demonstrations}, 2017, pp. 97–102.

\bibitem{airport}
M. Carisi \textit{et al.}, \enquote{Design and implementation of an airport chatbot},
in \textit{The 5th EAI International Conference on Smart Objects and Technologies for Social Good}, 2019, pp. 49–54.

\bibitem{commerce}
S. Angelov, and M. Lazarova, \enquote{E-commerce Distributed Chatbot System},
in \textit{The 9th Balkan Conference on Informatics}, 2019, pp. 1-8.

\bibitem{clustered}
H. Cuayáhuitl \textit{et al.}, \enquote{Deep Reinforcement Learning for Chatbots
Using Clustered Actions and Human-Likeness Rewards},
presented at International Joint Conference of Neural Networks, 2019.

\bibitem{generation}
J. Li \textit{et al.}, \enquote{Deep Reinforcement Learning for Dialogue Generation},
in \textit{The 2016 Conference on Empirical Methods in Natural Language Processing}, 2016, pp. 1192–1202.

\bibitem{gradient}
R. J. Williams, \enquote{Simple statistical gradient following algorithms for connectionist reinforcement learning},
in \textit{Machine Learning}, vol. 8, Hendrik Blockeel, 1992, pp. 229–256.

\bibitem{selfimproving}
E. Ricciardelli and D. Biswas, \enquote{Self-improving Chatbots based on Reinforcement Learning},
presented at 4th Multidisciplinary Conference on Reinforcement Learning and Decision Making, Montreal, Canada, 2019.

\bibitem{traininggochatbot}
M. Brenner, \enquote{Training a Goal-Oriented Chatbot with Deep Reinforcement Learning}.
Internet: \url{https://towardsdatascience.com/training-a-goal-oriented-chatbot-with-deep-reinforcement-learning-part-i-introduction-and-dce3af21d383}, Dec. 2, 2018.

\bibitem{endtoend}
Xiujun Li \textit{et al.}, \enquote{End-to-End Task-Completion Neural Dialogue Systems},
in \textit{The 8th International Joint Conference on Natural Language Processing}, Taipei, Taiwan, 2017, pp. 733–743.

% reference in chapter 3
\bibitem{reinforcementlearninganintroduction}
R. S. Sutton and A. G. Barto, \textit{Reinforcement Learning: An Introduction}.
Cambridge, MA: MIT Press, 2018.

\bibitem{introductiondeepqlearningpython}
A. Choudhary, \enquote{A Hands-On Introduction to Deep Q-Learning using OpenAI Gym in Python}.
Internet: \url{https://www.analyticsvidhya.com/blog/2019/04/introduction-deep-q-learning-python}, Apr. 18, 2019.

% reference in chapter 4
\bibitem{chatbothddoan}
Phạm Minh Hiếu, Cao Chánh Dương, \enquote{Phát triển một Chatbot thông minh để tư vấn hoạt động đoàn cho sinh viên},
Luận văn tốt nghiệp Đại học, Trường Đại học Bách Khoa TPHCM, 2020.

% reference other
\bibitem{refer1}
K. Shiruru, (2016, Sep.). \enquote{An Introduction to Artificial Neural Network}.
\textit{International Journal Of Advance Research And Innovative Ideas In Education}.
[Online]. 1(5), pp. 27-30.
Available: \url{https://www.researchgate.net/publication/319903816_AN_INTRODUCTION_TO_ARTIFICIAL_NEURAL_NETWORK}

\bibitem{refer5}
M. Mnasri, \enquote{Recent advances in conversational NLP: Towards the standardization of Chatbot building}.
Internet: \url{https://arxiv.org/pdf/1903.09025.pdf}, Mar. 21, 2019.

\bibitem{refer7}
V. Ilievski \textit{et al.}, \enquote{Goal-Oriented Chatbot Dialog Management Bootstrapping with Transfer Learning},
in \textit{The 27th International Joint Conference on Artificial Intelligence}, 2018, pp. 4115–4121.

\bibitem{refer9}
V. Ilievski, \enquote{Building Advanced Dialogue Managers for Goal-Oriented Dialogue Systems}.
Internet: \url{https://arxiv.org/pdf/1806.00780.pdf}, Jun. 3, 2018.

\bibitem{refer10}
J. Liu \textit{et al.}, \enquote{GoChat: Goal-oriented Chatbots with Hierarchical Reinforcement Learning},
presented at the 43rd International ACM SIGIR Conference on Research and Development in Information Retrieval, 2020.

\bibitem{refer11}
A. Bodirlau \textit{et al.}, \enquote{Cross-Domain Training for Goal-Oriented Conversational Agents},
in \textit{The International Conference on Recent Advances in Natural Language Processing}, Varna, Bulgaria, 2019, pp. 142–150.

\bibitem{refer12}
A. Xu \textit{et al.}, \enquote{A New Chatbot for Customer Service on Social Media},
in \textit{The 2017 CHI Conference on Human Factors in Computing Systems}, 2017, pp. 3506–3510.

\bibitem{refer13}
I. V. Serban \textit{et al.}, \enquote{A Deep Reinforcement Learning Chatbot}.
Internet: \url{https://arxiv.org/pdf/1709.02349.pdf}, Nov. 5, 2017.

\bibitem{refer14}
T. Schaul \textit{et al.}, \enquote{Prioritized Experience Replay},
presented at International Conference on Learning Representations, 2015.

\bibitem{refer15}
J. Gao \textit{et al.}, \enquote{Neural Approaches to Conversational AI},
in \textit{The 56th Annual Meeting of the Association for Computational Linguistics: Tutorial Abstracts},
Melbourne, Australia, 2019, pp. 2–7.

\end{thebibliography}
